Defending Against Web Application Attacks: Approaches, Challenges and Implications \vspace{-1mm}

### 2017-02-03 docs/paper/questioning.tex
updated figs (png) and citation numbers

\begin{figure}
\begin{center}
\leavevmode
\includegraphics[scale=0.52]{attack-tree-uml.pdf}
\end{center}
\vspace{-6mm}
\caption{\label{fig:taxonomy}A taxonomy of dynamic and domain-specific
language code injection attacks against web applications.}
\vspace{-6.5mm}
\end{figure}

@@

\begin{figure*}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.46]{attacks-steps-CSRF.pdf}
\end{center}
\vspace{-5.5mm}
\caption{\label{fig:attacks}Attack model for dynamic and domain specific
language code injection in web applications.
Transitions are labeled with the different attacks that use that path,
while the numbers next to attack labels denote the 
sequence of steps for a particular attack.
Points where different types of defenses
detect or prevent attacks are marked with an `X' symbol:
(1) {\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,
PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08,SSM10,HBBS14,SYMRHKM14,BCJPST15,GLSTMMR12},
(2) {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
(3) {\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05b,SMS13},
(4) {\sc db} (at the database):~\cite{BK04,LLW02,VMV05,CVMA07,GLSTMMR12,CPSPBCCSL12}.}
\vspace{-6mm}
\end{figure*}

@@

\begin{figure}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.50]{defenses.pdf}
\end{center}
\vspace{-5.8mm}
\caption{\label{fig:defenses}The basic categories of countermeasures
against web application attacks based on code
injection. For each approach we provide the references
that present corresponding mechanisms:
{\it Policy Enforcement}:~\cite{NSS06,JKK06a,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08,SSM10},
{\sc isr}:~\cite{BK04,JB07,GC09,APKLM10},
{\it Parse-Tree Validation}:~\cite{BWS05,SW06},
{\it Taint Tracking}:~\cite{HCF05,PB05,XBS06,NLC07,VFJKKV07,PMP11,SLMS14},
{\it Training}:~\cite{LLW02,HO05b,VMV05,JEP08,WPLKK09,MS09,MKLS11},
{\it Hybrid}:~\cite{BV08,LV09,SMS13,HBBS14,SYMRHKM14,BCJPST15,CVMA07,GLSTMMR12,CPSPBCCSL12}.}
\vspace{-5.5mm}
\end{figure}

@@

  &   {\sc sqlg}uard~\cite{BWS05} & 305 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% ({\sc s}) & {\sc sql}i \\
  &   {\sc sqlc}heck~\cite{SW06} & 473 & (36848,7648,0,0)\_r & 3ms per query ({\sc s}) & {\sc sql}i \\

@@

  &   {\sc dsi}~\cite{NSS06} & 168 & (5268,{\sc nq},{\sc nq},85)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
  &   NoForge~\cite{JKK06a} & 151 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} ({\sc s}) & {\sc csrf} \\
  &   Noxes~\cite{KJKV09} & 58 & (3,{\sc na},{\sc na},0)\_r & {\sc na} ({\sc c}) & {\sc xss} \\

@@

  &   {\sc beep}~\cite{TNH07} & 335 & (61,{\sc na},{\sc na},0)\_r & 14.4\% ({\sc c}) & {\sc xss} \\
  &   BrowserShield~\cite{RDWDE07} & 263 & (19,{\sc nq},0,0,)\_r & 8\% ({\sc s}) & {\sc xss} \\ 
  &   CoreScript~\cite{YCIS07} & 199 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} ({\sc c}) & {\sc xss} \\
  &   {\it {\sc soma}}~\cite{OWVS08} & 56 & (5,{\sc na},{\sc na},0)\_s & 5.58\% ({\sc c}) & {\sc xss}, {\sc csrf} \\

@@

  &   Phung et al.~\cite{PSC09} & 101 & (37,{\sc na},{\sc na},4)\_r & 5.37\% ({\sc c}) & {\sc xss} \\

@@

  &   CsFire~\cite{DDHPJ10} & 46 & (419582,1141807,0,3)\_r\tnote{5} & {\sc na} ({\sc c}) & {\sc csrf} \\
  &   {\sc csp}~\cite{SSM10} & 117 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} ({\sc c}) & {\sc xss}, {\sc csrf} \\

@@

  &   WebJail~\cite{VDDPJ11} & 45 & (2,{\sc na},{\sc na},1)\_{\bf ?} & $\sim$6.89ms ({\sc c}) & {\sc xss} \\

@@

  &   {\sc sql}rand~\cite{BK04} & 365 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} ({\sc s}) & {\sc sql}i \\
  &   {\sc sm}ask~\cite{JB07} & 28 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql}i, {\sc xss} \\
  &   Noncespaces~\cite{GC09} & 132 & (6,{\sc na},{\sc na},0)\_r &  2\% ({\sc s}) & {\sc xss} \\ 
  &   x{\sc js}~\cite{APKLM10} & 20 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40ms ({\sc c}) & {\sc xss} \\

@@

  &   Haldar et al.~\cite{HCF05} & 208 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
  &   {\sc csse}~\cite{PB05} & 347 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% ({\sc s}) & {\sc sql}i, {\sc xp}athi, {\sc xss} \\

@@

  &   Xu et al.~\cite{XBS06} & 346 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
  &   {\sc wasc}~\cite{NLC07} & 32 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% ({\sc s}) & {\sc sql}i, {\sc xss} \\
  &   Vogt et al.~\cite{VFJKKV07} & 400 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} ({\sc c}) & {\sc xss} \\
  &   {\sc php} Aspis~\cite{PMP11} & 20 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql}i and {\sc php}i, {\sc xss} \\
  &   Stock et al.~\cite{SLMS14} & 15 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc c}) & {\sc dom}-based {\sc xss} \\

@@

  &   {\sc didafit}~\cite{LLW02} & 190 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} ({\sc s}) & {\sc sql}i \\
  &   {\sc amnesia}~\cite{HO05b} & 474 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql}i \\ 
  &   libAnomaly~\cite{VMV05} & 259 & (9,15987,60,0)\_r & 0.20--1ms per query ({\sc s}) & {\sc sql}i \\
  &   {\sc xssds}~\cite{JEP08} & 85 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
  &   {\sc swap}~\cite{WPLKK09} & 68 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 261ms ({\sc s}) & {\sc xss} \\ 
  &   {\sc sd}river~\cite{MS09,MKLS11} & 28 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql}i and {\sc xp}athi \\

@@

  &   {\sc xss-guard}~\cite{BV08} & 132 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% ({\sc c}) & {\sc xss} \\
  &   Blueprint~\cite{LV09} & 152 & (94,{\sc na},{\sc na},0)\_r & 13.6\% ({\sc c}) & {\sc xss} \\
  &   Diglossia~\cite{SMS13} & 13 & (25,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and {\sc json}i \\
  &   {\sc jsf}low~\cite{HBBS14} & 62 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r

@@

  &   {\sc cowl}~\cite{SYMRHKM14} & 27 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r

@@

  &   Bauer et al.~\cite{BCJPST15} & 5 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}

@@

  &   {\sc sif}~\cite{CVMA07} & 146 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}

@@

  &   Hails~\cite{GLSTMMR12} & 78 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r

@@

  &   Aeolus~\cite{CPSPBCCSL12} & 52 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}

@@

\begin{figure}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.40]{barchart.pdf}
\end{center}
\vspace{-6mm}
\caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
used for testing of web attack defenses.
Specifically, the publications that used a particular source are as follows:
{\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
Bugtraq~\cite{PB05,KJKV09,JEP08},
{\sc xss}ed.com~\cite{NSS06,APKLM10},
ha.ckers.org~\cite{TNH07,PSC09,LV09},
Microsoft~\cite{RDWDE07}.}
\vspace{-6mm}
\end{figure}

@@

\bibliographystyle{IEEEtran}
\bibliography{questioning}
\vspace{-1.2mm}

\section*{Author Biographies}
\vspace{-1.1mm}
\noindent
{\bf Dimitris Mitropoulos} is a Postdoctoral Researcher
in the Computer Science Department
at Columbia University.
He holds a PhD ('14) in Cyber Security from the
Athens University of Economics and Business.
His research interests include application security,
systems security and software engineering.

>>>>

\begin{figure}
\begin{center}
\leavevmode
\includegraphics[scale=0.52]{attack-tree.png}
\end{center}
\vspace{-6mm}
\caption{\label{fig:taxonomy}A taxonomy of dynamic and domain-specific
language code injection attacks against web applications.}
\vspace{-6.5mm}
\end{figure}

@@

\begin{figure*}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.46]{attacks-steps.png}
\end{center}
\vspace{-5.5mm}
\caption{\label{fig:attacks}Attack model for dynamic and domain specific
language code injection in web applications.
Transitions are labeled with the different attacks that use that path,
while the numbers next to attack labels denote the 
sequence of steps for a particular attack.
Points where different types of defenses
detect or prevent attacks are marked with an `X' symbol:
(1) {\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,
PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08,SSM10,HBBS14,SYMRHKM14,BCJPST15,GLSTMMR12},
(2) {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
(3) {\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05b,SMS13},
(4) {\sc db} (at the database):~\cite{BK04,LLW02,VMV05,CVMA07,GLSTMMR12,CPSPBCCSL12}.}
\vspace{-6mm}
\end{figure*}

@@

\begin{figure}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.50]{defenses.png}
\end{center}
\vspace{-5.8mm}
\caption{\label{fig:defenses}The basic categories of countermeasures
against web application attacks based on code
injection. For each approach we provide the references
that present corresponding mechanisms:
{\it Policy Enforcement}:~\cite{NSS06,JKK06a,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08,SSM10},
{\sc isr}:~\cite{BK04,JB07,GC09,APKLM10},
{\it Parse-Tree Validation}:~\cite{BWS05,SW06},
{\it Taint Tracking}:~\cite{HCF05,PB05,XBS06,NLC07,VFJKKV07,PMP11,SLMS14},
{\it Training}:~\cite{LLW02,HO05b,VMV05,JEP08,WPLKK09,MS09,MKLS11},
{\it Hybrid}:~\cite{BV08,LV09,SMS13,HBBS14,SYMRHKM14,BCJPST15,CVMA07,GLSTMMR12,CPSPBCCSL12}.}
\vspace{-5.5mm}
\end{figure}

@@

  &   {\sc sqlg}uard~\cite{BWS05} & 368 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% ({\sc s}) & {\sc sql}i \\
  &   {\sc sqlc}heck~\cite{SW06} & 547 & (36848,7648,0,0)\_r & 3ms per query ({\sc s}) & {\sc sql}i \\

@@

  &   {\sc dsi}~\cite{NSS06} & 188 & (5268,{\sc nq},{\sc nq},85)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
  &   NoForge~\cite{JKK06a} & 166 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} ({\sc s}) & {\sc csrf} \\
  &   Noxes~\cite{KJKV09} & 69 & (3,{\sc na},{\sc na},0)\_r & {\sc na} ({\sc c}) & {\sc xss} \\

@@

  &   {\sc beep}~\cite{TNH07} & 362 & (61,{\sc na},{\sc na},0)\_r & 14.4\% ({\sc c}) & {\sc xss} \\
  &   BrowserShield~\cite{RDWDE07} & 273 & (19,{\sc nq},0,0,)\_r & 8\% ({\sc s}) & {\sc xss} \\ 
  &   CoreScript~\cite{YCIS07} & 212 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} ({\sc c}) & {\sc xss} \\
  &   {\it {\sc soma}}~\cite{OWVS08} & 65 & (5,{\sc na},{\sc na},0)\_s & 5.58\% ({\sc c}) & {\sc xss}, {\sc csrf} \\

@@

  &   Phung et al.~\cite{PSC09} & 124 & (37,{\sc na},{\sc na},4)\_r & 5.37\% ({\sc c}) & {\sc xss} \\

@@

  &   CsFire~\cite{DDHPJ10} & 52 & (419582,1141807,0,3)\_r\tnote{5} & {\sc na} ({\sc c}) & {\sc csrf} \\
  &   {\sc csp}~\cite{SSM10} & 143 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} ({\sc c}) & {\sc xss}, {\sc csrf} \\

@@

  &   WebJail~\cite{VDDPJ11} & 53 & (2,{\sc na},{\sc na},1)\_{\bf ?} & $\sim$6.89ms ({\sc c}) & {\sc xss} \\

@@

  &   {\sc sql}rand~\cite{BK04} & 428 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} ({\sc s}) & {\sc sql}i \\
  &   {\sc sm}ask~\cite{JB07} & 31 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql}i, {\sc xss} \\
  &   Noncespaces~\cite{GC09} & 146 & (6,{\sc na},{\sc na},0)\_r &  2\% ({\sc s}) & {\sc xss} \\ 
  &   x{\sc js}~\cite{APKLM10} & 29 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40ms ({\sc c}) & {\sc xss} \\

@@

  &   Haldar et al.~\cite{HCF05} & 234 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
  &   {\sc csse}~\cite{PB05} & 387 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% ({\sc s}) & {\sc sql}i, {\sc xp}athi, {\sc xss} \\

@@

  &   Xu et al.~\cite{XBS06} & 368 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
  &   {\sc wasc}~\cite{NLC07} & 37 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% ({\sc s}) & {\sc sql}i, {\sc xss} \\
  &   Vogt et al.~\cite{VFJKKV07} & 490 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} ({\sc c}) & {\sc xss} \\
  &   {\sc php} Aspis~\cite{PMP11} & 26 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql}i and {\sc php}i, {\sc xss} \\
  &   Stock et al.~\cite{SLMS14} & 23 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc c}) & {\sc dom}-based {\sc xss} \\

@@

  &   {\sc didafit}~\cite{LLW02} & 208 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} ({\sc s}) & {\sc sql}i \\
  &   {\sc amnesia}~\cite{HO05b} & 551 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql}i \\ 
  &   libAnomaly~\cite{VMV05} & 310 & (9,15987,60,0)\_r & 0.20--1ms per query ({\sc s}) & {\sc sql}i \\
  &   {\sc xssds}~\cite{JEP08} & 96 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
  &   {\sc swap}~\cite{WPLKK09} & 83 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 261ms ({\sc s}) & {\sc xss} \\ 
  &   {\sc sd}river~\cite{MS09,MKLS11} & 36 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql}i and {\sc xp}athi \\

@@

  &   {\sc xss-guard}~\cite{BV08} & 153 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% ({\sc c}) & {\sc xss} \\
  &   Blueprint~\cite{LV09} & 187 & (94,{\sc na},{\sc na},0)\_r & 13.6\% ({\sc c}) & {\sc xss} \\
  &   Diglossia~\cite{SMS13} & 23 & (25,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and {\sc json}i \\
  &   {\sc jsf}low~\cite{HBBS14} & 72 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r

@@

  &   {\sc cowl}~\cite{SYMRHKM14} & 41 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r

@@

  &   Bauer et al.~\cite{BCJPST15} & 10 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}

@@

  &   {\sc sif}~\cite{CVMA07} & 155 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}

@@

  &   Hails~\cite{GLSTMMR12} & 92 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r

@@

  &   Aeolus~\cite{CPSPBCCSL12} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}

@@

\begin{figure}[t]
\begin{center}
\leavevmode
\includegraphics[scale=0.40]{barchart.png}
\end{center}
\vspace{-6mm}
\caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
used for testing of web attack defenses.
Specifically, the publications that used a particular source are as follows:
{\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
Bugtraq~\cite{PB05,KJKV09,JEP08},
{\sc xss}ed.com~\cite{NSS06,APKLM10},
ha.ckers.org~\cite{TNH07,PSC09,LV09},
Microsoft~\cite{RDWDE07}.}
\vspace{-6mm}
\end{figure}

@@

\bibliographystyle{IEEEtran}
\bibliography{questioning}
\vspace{-1.6mm}

\section*{Author Biographies}
\vspace{-0.7mm}
\noindent
{\bf Dimitris Mitropoulos} is a Postdoctoral Researcher
in the Computer Science Department
at Columbia University.
He holds a PhD ('14) in Cyber Security from the
Athens University of Economics and Business.
His research interests include application security,
systems security and software engineering.
